ANTs-Flavored Tract-Based Spatial Statistics

### 2011-03-24 ANTsTBSS/paper.tex
Minor edits, new figure.

Comparison of areas of significant difference between the two groups for both methodologies can be seen on several corresponding axial slices in Figure \ref{fig:hoonData}.  The majority of the areas of significance overlap between the two analyses although the yellow arrow points to one difference situated in the right frontal lobe.

@@

\begin{figure}
\begin{tabular}{c}
  \includegraphics[width=80mm]{hoonData2.pdf}
\end{tabular}
\caption{Results of TBSS analysis using both the ANTs template-based approach (top row) and the standard TBSS protocol (bottom row).  Axial slices were chosen based on visual assessment of correspondence in both the ANTs template and MNI 152 template.
On the left is the thresholded skeleton overlaid on the mean FA image.  
On the right, significant areas of difference are given in red ($p \leq 0.01$ after the threshold-free cluster enhancement correction described in \cite{Smith2009}).  The yellow arrow points to an area of significant difference in the peripheral white matter found using ANTs-TBSS.
}
\label{fig:hoonData}
\end{figure}

>>>>

%Comparison of areas of significant difference between the two groups for both methodologies can be seen on several corresponding axial slices in Figure \ref{fig:hoonData}.  The majority of the areas of significance overlap between the two analyses although the yellow arrow points to one difference situated in the right frontal lobe.

@@

%\begin{figure}
%\begin{tabular}{c}
%  \includegraphics[width=80mm]{hoonData2.pdf}
%\end{tabular}
%\caption{Results of TBSS analysis using both the ANTs template-based approach (top row) and the standard TBSS protocol (bottom row).  Axial slices were chosen based on visual assessment of correspondence in both the ANTs template and MNI 152 template.
%On the left is the thresholded skeleton overlaid on the mean FA image.  
%On the right, significant areas of difference are given in red ($p \leq 0.01$ after the threshold-free cluster enhancement correction described in \cite{Smith2009}).  The yellow arrow points to an area of significant difference in the peripheral white matter found using ANTs-TBSS.
%}
%\label{fig:hoonData}
%\end{figure}
